Converging High-Throughput and High-Performance Computing Paradigms: \\ A Case Study of Using Abstractions to Bridge the Divide

### 2017-03-19 PandaEvolution.tex
Ongoing references

Usually, backfill availability is a fraction of the total capacity of the queue
but the size of Titan mitigates this limitation. Every year, about 10\% of
Titan's capacity remains unused~\cite{titan_utilization}, corresponding to an
average of 30,000 unused cores. This equals approximately 270M core hours per
year, roughly 30\% of the overall capacity of WLCG.

@@

MPI scripts are submitted to Titan's PBS batch system via
RADICAL-SAGA~\cite{radical-saga}, a Python module, compliant with the OGF GFD.90
SAGA specification~\cite{saga-spec}. The Simple API for Grid Applications (SAGA)
offers a unified interface to diverse job schedulers and file transferring
services. In this way, SAGA provides an interoperability layer that lowers the
complexity of using distributed infrastructures. Behind the API façade,
RADICAL-SAGA implements a adaptor architecture: each adaptor interface the SAGA
API with different middleware systems and services, including the PBS batch
scheduler of Titan.

>>>>

Usually, backfill availability is a fraction of the total capacity of the queue
but the size of Titan mitigates this limitation. Every year, about 10\% of
Titan's capacity remains unused, corresponding to an average of 30,000 unused
cores. This equals approximately 270M core hours per year, roughly 30\% of the
overall capacity of WLCG.

@@

MPI scripts are submitted to Titan's PBS batch system via
RADICAL-SAGA~\cite{radical-saga_url}, a Python module, compliant with the OGF
GFD.90 SAGA specification~\cite{goodale2008simple}. The Simple API for Grid
Applications (SAGA) offers a unified interface to diverse job schedulers and
file transferring services. In this way, SAGA provides an interoperability layer
that lowers the complexity of using distributed infrastructures. Behind the API
façade, RADICAL-SAGA implements a adaptor architecture: each adaptor interface
the SAGA API with different middleware systems and services, including the PBS
batch scheduler of Titan.

### 2017-03-19 PandaOverview.tex
Iteration 4 and 5 adding Sergey's data
Ongoing references

PanDA's application model primarily assumes single tasks, workloads and
workflows. Tasks represent a set of operations performed on a set of events,
stored across input files. Tasks can be decomposed into jobs, where each job
represents the task's set of operations and a partition of the task's events.
Since 2005, a certain amount of parallelism has been progressively introduced
for jobs~\cite{multithreaded_jobs} but, so far, no MPI jobs have been considered
for production. Jobs are supposed to be relatively self-contained, capable of
setting up their own execution environment or having a minimal set of common
dependences. Different types of job payload (i.e., executable) are assumed, both
in terms of user-defined batch scripts or application frameworks for group of
users.

@@

The implementation of PanDA consists of several interconnected subsystems, most
of them built from off-the-shelf and Open Source components. At a high level,
PanDA's architecture has six main subsystems: PanDA Server, AutoPyFactory, PanDA
Pilot, PanDA Monitoring, JEDI, and Event Service. Subsystems communicate via
dedicated API or http messaging. Databases are used to store eventful entities
like tasks, jobs and events, and to store information about resources, logs, and
accounting. Each subsystems is implemented by one or more modules as shown in
Figure~\ref{fig:architecture}. In the following, we briefly describe the overall
architecture of PanDA and its components. The description provides all the
details required to understand how HPC resources have been integrated within
PanDA (\ref{sec:integration}). For a more detailed description of PanDA
architecture see~\cite{wiki, papers}.

@@

PanDA Pilot implements the pilot paradigm~\cite{pilot_review}, decoupling
resource acquisition from job execution via multi-stage scheduling. This has
several benefits, including increasing throughput by lowering the time taken to
queue and schedule jobs; enabling both concurrent and sequential job execution
depending on the number of cores available to the pilot and the time for which
it remains available; and exposing a unified and consistent interface for the
scheduling of jobs, independent from the middleware of the site on which the
pilot has been instantiated.

>>>>

PanDA's application model primarily assumes single tasks, workloads and
workflows. Tasks represent a set of operations performed on a set of events,
stored across input files. Tasks can be decomposed into jobs, where each job
represents the task's set of operations and a partition of the task's events.
Since 2005, a certain amount of parallelism has been progressively introduced
for jobs~\cite{crooks2012multi} but, so far, no MPI jobs have been considered
for production. Jobs are supposed to be relatively self-contained, capable of
setting up their own execution environment or having a minimal set of common
dependences. Different types of job payload (i.e., executable) are assumed, both
in terms of user-defined batch scripts or application frameworks for group of
users.

@@

The implementation of PanDA consists of several interconnected subsystems, most
of them built from off-the-shelf and Open Source components. At a high level,
PanDA's architecture has six main subsystems: PanDA Server, AutoPyFactory, PanDA
Pilot, PanDA Monitoring, JEDI, and Event Service. Subsystems communicate via
dedicated API or http messaging. Databases are used to store eventful entities
like tasks, jobs and events, and to store information about resources, logs, and
accounting. Each subsystems is implemented by one or more modules as shown in
Figure~\ref{fig:architecture}. In the following, we briefly describe the overall
architecture of PanDA and its components. The description provides all the
details required to understand how HPC resources have been integrated within
PanDA (\ref{sec:integration}).

% For a more detailed description of PanDA architecture see~\cite{wiki, papers}.

@@

PanDA Pilot implements the pilot paradigm~\cite{turilli2015comprehensive},
decoupling resource acquisition from job execution via multi-stage scheduling.
This has several benefits, including increasing throughput by lowering the time
taken to queue and schedule jobs; enabling both concurrent and sequential job
execution depending on the number of cores available to the pilot and the time
for which it remains available; and exposing a unified and consistent interface
for the scheduling of jobs, independent from the middleware of the site on which
the pilot has been instantiated.
